Phase paper outline

### 2014-06-05 Manuscript/Phase_detectors_outline.tex
added some notes

\documentclass{article}
\title{Phase paper outline your mom last night}
\author{}
\date{}
\begin{document}
\maketitle

@@

\subsection*{Potential physiology journals}
The paper should have this structure:\cite{muller_estimation_2003}
\begin{itemize}
\item Acta physiologica
\item Physiological Reports
\item AJP Heart/regulatory - Innovative methodology
\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
\item The Journal of General Physiology - methods and approaches
\item Physiological measurement
\item Journal of experimental physiology
\item Journal of Applied Phyiology
\item E-Life
\end{itemize}

@@

\subsection*{Time-averaged phase, or Frequency domain phase}

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item Blood pressure and heart rate
	\begin{itemize}
	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.  With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.  The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation; Stewart et al., 2000).  Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.  
	\end{itemize}
\item Something about SCG or ECG ?
\item Cerebral blood flow ?
\end{itemize}

@@

	\subsection*{Figures}
	\begin{enumerate}
	\item Simulation
		\begin{enumerate}
		\item Time series of raw simulated data + added noise
		\item Power spectrum of the data
		\item Time-domain phase 
		\item Accuracy of each detector at a range of signal to noise ratios
		\end{enumerate}
	\item Rat data
		\begin{enumerate}
		\item BP and cortical perfusion
		\item Phase interactions between two or three regions on the renal surface
		\end{enumerate}
	\item{Human data}
		\begin{enumerate}
		\item BP and heart rate
		\item Use phase to find the lag between a change in bp and a change in heart rate
		\end{enumerate}
	\end{enumerate}

	\subsection*{Tables}
		\begin{enumerate}
			\item Simulation
			\begin{enumerate}
			\item Noise conversation
				\begin{itemize}
					\item Add gaussian noise from snr=$\infty$ up to when it breaks down.
					\item It breaks down when 0 is not in the 95\% confidence interval of Bland-Altman-style statistics.		
				\end{itemize}
			\item Chirp (Frequency from point A to point B)
				\begin{itemize}
					\item Specifically to talk about limits to the bandpass filtering needed for the Hilbert method.
				\end{itemize}
			\item Length of signal
				\begin{itemize}
					\item Shorten the signal until techniques breakdown.
					\item Relative to frequency.
				\end{itemize}		
			\end{enumerate}
			\item Physiological Data

		\end{enumerate}

\bibliographystyle{plain}
\bibliography{OutlineBib}

>>>>

\documentclass{article}
\title{Phase paper outline}
\author{}
\date{}
\begin{document}
\maketitle

@@

\subsection*{Potential physiology journals}

\begin{itemize}
\item Acta physiologica
\item Physiological Reports
\item AJP Heart/regulatory - Innovative methodology
\item The Journal of Physiology - techniques for physiology \textit{I think this kind of thing might be best}
\item The Journal of General Physiology - methods and approaches
\item Physiological measurement
\item Journal of experimental physiology
\end{itemize}

@@

\subsection*{Frequency domain phase}

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item Blood pressure and heart rate
	\begin{itemize}
	\item Phase lag between changes in blood pressure and changes in heart rate

The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.  With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.  The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation; Stewart et al., 2000).  Therefore, the phase relationship between these two signals is an important outcome measure for cardiovascular testing.

	\end{itemize}
\item Something about SCG or ECG ?
\item Cerebral blood flow ?
\end{itemize}

@@

	\subsection*{Figures}
	\begin{enumerate}
	\item Simulation
		\begin{enumerate}
		\item Time series of raw simulated data
		\item Time-domain phase 
		\item Accuracy of each detector at a range of signal to noise ratios
		\end{enumerate}
	\item Rat data
		\begin{enumerate}
		\item BP and cortical perfusion
		\item Phase interactions between two or three regions on the renal surface
		\end{enumerate}
	\item{Human data}
		\begin{enumerate}
		\item BP and heart rate
		\item Use phase to find the lag between a change in bp and a change in heart rate
		\end{enumerate}
	\end{enumerate}
